Short Paper

### 2020-10-23 Paper/journal-article/journal-article.Rmd
updates to paper

  It consists of two paragraphs.

@@

@@

@@

@@

>>>>

@@

<!-- Keywords -->
<!-- ======== -->

<!-- Highlights -->
<!-- ======== -->

@@

\vspace{0.3cm}

@@

\vspace{0.3cm}

The problem formulations outlined above look at the network as a whole when attempting to improve it. An alternative approach is to identify the different sub-networks that exist within the larger network, and work on improving each separately. Trip patterns in a city are not uniformly distributed geographically, and *community finding* methods have been used to partition study areas into localized areas that experience a disproportionate number of trips within them. @akbarzadeh2018designing use a modularity maximization approach [@blondel2008fast] on taxi trip data to identify 7 different communities in the city of Isfahan, Iran. An optimization problem is then formulated to connect nodes within each community with cycling infrastructure. The emphasis is on connectivity within the communities, not between them. @bao2017planning adopt a similar methodology, but use hierarchical clustering to specify the desired number of clusters. They use a greedy network expansion algorithm, where the link with the highest benefit/cost ratio in each cluster is selected, and the network is grown by adding neighboring links to the solution until a budget limit is met. The benefit is the flow on the link, and each link is assigned a cost based on current road conditions.

## Underlying Ethical Principles

The methodologies in Section **How do I cite a section??** are underpinned by different ethical principles, even though these principles are not explicitly acknowledged by the authors. This is important since different ethical principles constitute different problem formulations and targets. Broadly speaking, transport appraisal can be based on either utilitarian or egalitarian principles. The former seeks to maximize the overall benefit, while the latter is concerned with a fair distribution of benefits [@jafino2020transport]. @nahmias2017integrating criticize the utilitarian approach that has been historically popular in the evaluation of transport investments, explaining how the maximization of overall benefit fails to account for the distribution of that benefit among communities or individuals. @lucas2016method explain how transport studies have traditionally looked at the bigger picture without studying the distribution of investments on the different parts of the study area, and go on to propose an egalitarian approach that ensures the dis-aggregation of transport policy benefits across the study area. @pereira2017distributive also emphasize the need for a more egalitarian approach to transport planning. They highlight accessibility as a cornerstone of distributive justice, and contend that policies should aim to distribute investments in a way that minimizes spatial variations in accessibility. This research attempts to provide a methodology that is grounded in egalitarian principles. **Write some more here**

@@

Overarching Policies
====================

While segregated, connected, and direct cycling infrastructure is key to achieving high levels of cycling, research has shown that it cannot exist in a vacuum. @wardman2007factors developed a mode choice model for the UK and their results showed that improved cycling infrastructure on its own only had modest impacts on mode shift, and even the unlikely scenario of all urban routes being serviced by segregated bike lanes was forecast to increase cycling mode share by only 3\%. 
However, cities that invest in more comprehensive cycling projects show a more significant increase in the number of cyclists as well as the cycling mode share [@pucher2010infrastructure]. These cities do not just focus on infrastructure, but on general policies as well as restricting car use. Evaluation of policies in Denmark and Germany and the Netherlands has shown that their high cycling mode share is down to a broader set of policies that also include traffic calming, cycling rights of way, bike parking, integration with the public transport network, and making driving cars both expensive and inconvenient [@pucher2008making]. While these policies are outside the scope of this research, it is important to recognize their key role in bringing about an increase in levels of cycling.

### 2020-10-23 Paper/journal-article/journal-article.tex
updates to paper

  \begin{abstract}
  This is the abstract.

  It consists of two paragraphs.
  \end{abstract}

@@

@@

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-aldred2019impacts}{}%
Aldred, R., Croft, J., Goodman, A., 2019. Impacts of an active travel
intervention with a cycling focus in a suburban context: One-year
findings from an evaluation of london's in-progress mini-hollands
programme. Transportation research part A: policy and practice 123,
147--169.

@@

@@

@@

@@

@@

>>>>

  \begin{abstract}
  This is the abstract.
  \end{abstract}

@@

\vspace{0.3cm}

The problem formulations outlined above look at the network as a whole
when attempting to improve it. An alternative approach is to identify
the different sub-networks that exist within the larger network, and
work on improving each separately. Trip patterns in a city are not
uniformly distributed geographically, and \emph{community finding}
methods have been used to partition study areas into localized areas
that experience a disproportionate number of trips within them.
Akbarzadeh et al. (2018) use a modularity maximization approach (Blondel
et al., 2008) on taxi trip data to identify 7 different communities in
the city of Isfahan, Iran. An optimization problem is then formulated to
connect nodes within each community with cycling infrastructure. The
emphasis is on connectivity within the communities, not between them.
Bao et al. (2017) adopt a similar methodology, but use hierarchical
clustering to specify the desired number of clusters. They use a greedy
network expansion algorithm, where the link with the highest
benefit/cost ratio in each cluster is selected, and the network is grown
by adding neighboring links to the solution until a budget limit is met.
The benefit is the flow on the link, and each link is assigned a cost
based on current road conditions.

\hypertarget{underlying-ethical-principles}{%
\subsection{Underlying Ethical
Principles}\label{underlying-ethical-principles}}

The methodologies in Section \textbf{How do I cite a section??} are
underpinned by different ethical principles, even though these
principles are not explicitly acknowledged by the authors. This is
important since different ethical principles constitute different
problem formulations and targets. Broadly speaking, transport appraisal
can be based on either utilitarian or egalitarian principles. The former
seeks to maximize the overall benefit, while the latter is concerned
with a fair distribution of benefits (Jafino et al., 2020).
Nahmias-Biran et al. (2017) criticize the utilitarian approach that has
been historically popular in the evaluation of transport investments,
explaining how the maximization of overall benefit fails to account for
the distribution of that benefit among communities or individuals. Lucas
et al. (2016) explain how transport studies have traditionally looked at
the bigger picture without studying the distribution of investments on
the different parts of the study area, and go on to propose an
egalitarian approach that ensures the dis-aggregation of transport
policy benefits across the study area. Pereira et al. (2017) also
emphasize the need for a more egalitarian approach to transport
planning. They highlight accessibility as a cornerstone of distributive
justice, and contend that policies should aim to distribute investments
in a way that minimizes spatial variations in accessibility. This
research attempts to provide a methodology that is grounded in
egalitarian principles. \textbf{Write some more here}

@@

\hypertarget{overarching-policies}{%
\section{Overarching Policies}\label{overarching-policies}}

While segregated, connected, and direct cycling infrastructure is key to
achieving high levels of cycling, research has shown that it cannot
exist in a vacuum. Wardman et al. (2007) developed a mode choice model
for the UK and their results showed that improved cycling infrastructure
on its own only had modest impacts on mode shift, and even the unlikely
scenario of all urban routes being serviced by segregated bike lanes was
forecast to increase cycling mode share by only 3\%. However, cities
that invest in more comprehensive cycling projects show a more
significant increase in the number of cyclists as well as the cycling
mode share (Pucher et al., 2010). These cities do not just focus on
infrastructure, but on general policies as well as restricting car use.
Evaluation of policies in Denmark and Germany and the Netherlands has
shown that their high cycling mode share is down to a broader set of
policies that also include traffic calming, cycling rights of way, bike
parking, integration with the public transport network, and making
driving cars both expensive and inconvenient (Pucher and Buehler, 2008).
While these policies are outside the scope of this research, it is
important to recognize their key role in bringing about an increase in
levels of cycling.

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-akbarzadeh2018designing}{}%
Akbarzadeh, M., Mohri, S.S., Yazdian, E., 2018. Designing bike networks
using the concept of network clusters. Applied network science 3, 12.

\leavevmode\hypertarget{ref-aldred2019impacts}{}%
Aldred, R., Croft, J., Goodman, A., 2019. Impacts of an active travel
intervention with a cycling focus in a suburban context: One-year
findings from an evaluation of london's in-progress mini-hollands
programme. Transportation research part A: policy and practice 123,
147--169.

\leavevmode\hypertarget{ref-bao2017planning}{}%
Bao, J., He, T., Ruan, S., Li, Y., Zheng, Y., 2017. Planning bike lanes
based on sharing-bikes' trajectories, in: Proceedings of the 23rd Acm
Sigkdd International Conference on Knowledge Discovery and Data Mining.
pp. 1377--1386.

\leavevmode\hypertarget{ref-blondel2008fast}{}%
Blondel, V.D., Guillaume, J.-L., Lambiotte, R., Lefebvre, E., 2008. Fast
unfolding of communities in large networks. Journal of statistical
mechanics: theory and experiment 2008, P10008.

@@

\leavevmode\hypertarget{ref-jafino2020transport}{}%
Jafino, B.A., Kwakkel, J., Verbraeck, A., 2020. Transport network
criticality metrics: A comparative analysis and a guideline for
selection. Transport Reviews 40, 241--264.

@@

\leavevmode\hypertarget{ref-lucas2016method}{}%
Lucas, K., Van Wee, B., Maat, K., 2016. A method to evaluate equitable
accessibility: Combining ethical theories and accessibility-based
approaches. Transportation 43, 473--490.

@@

\leavevmode\hypertarget{ref-nahmias2017integrating}{}%
Nahmias-Biran, B.-h., Martens, K., Shiftan, Y., 2017. Integrating equity
in transportation project assessment: A philosophical exploration and
its practical implications. Transport reviews 37, 192--210.

@@

\leavevmode\hypertarget{ref-pereira2017distributive}{}%
Pereira, R.H., Schwanen, T., Banister, D., 2017. Distributive justice
and equity in transportation. Transport reviews 37, 170--191.

\leavevmode\hypertarget{ref-pucher2008making}{}%
Pucher, J., Buehler, R., 2008. Making cycling irresistible: Lessons from
the netherlands, denmark and germany. Transport reviews 28, 495--528.

\leavevmode\hypertarget{ref-pucher2010infrastructure}{}%
Pucher, J., Dill, J., Handy, S., 2010. Infrastructure, programs, and
policies to increase bicycling: An international review. Preventive
medicine 50, S106--S125.

@@

\leavevmode\hypertarget{ref-wardman2007factors}{}%
Wardman, M., Tight, M., Page, M., 2007. Factors influencing the
propensity to cycle to work. Transportation Research Part A: Policy and
Practice 41, 339--350.
